The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-13 paper/ms.tex
round out red clump section
hipparcos

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like tihs or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$. In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.

@@

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}.

>>>>

\subsection{Sample}
\label{sample}

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.

@@

@@

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}. While precise characterization of these stars to the necessary degree is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.
